|

### 2023-04-11 paper.Rmd
correct caption

```{r polypower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for non-linear patterns (uniform fitted values only). The power curves are estimated using logistic regression, and the horizontal lines of dots represent non-reject and reject results from visual tests for each lineup. The visual test has multiple power curves estimated from bootstrap samples. The row of scatterplots plots at the bottom are examples of residual plots corresponding to the specific effect sizes marked by vertical lines in the main plot.", dev = 'png', dpi = 450}

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating non-reject and reject in visual testing of lineups. The multiple lines for the visual test arise from estimating the power on many bootstrap samples. The row of scatterplots plots at the bottom are examples of residual plots corresponding to the specific effect sizes marked by vertical lines in the main plot.", dev = 'png', dpi = 450}

>>>>

```{r polypower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for non-linear patterns (uniform fitted values only). The power curves are estimated using logistic regression, and the horizontal lines of dots represent non-reject and reject results from visual tests for each lineup. The visual test has multiple power curves estimated from bootstrap samples. The row of scatterplots at the bottom are examples of residual plots corresponding to the specific effect sizes marked by vertical lines in the main plot.", dev = 'png', dpi = 450}

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating non-reject and reject in visual testing of lineups. The multiple lines for the visual test arise from estimating the power on many bootstrap samples. The row of scatterplots at the bottom are examples of residual plots corresponding to the specific effect sizes marked by vertical lines in the main plot.", dev = 'png', dpi = 450}
